---
title: "UFO_"
author: "Jack Chu"
date: "2023-02-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## The following code is my way of scraping the UFO Sighting Reports (from 1980-2022) from the National UFO Report Center website.
## I later grouped each of them so I could know the frequency of the cities that have UFO sightings. Eventually, I organized them into a 
## data frame so I ccould use it for data visualization purposes in Tableau.


## UFO Sightings Cities (1980- present)
## (Scraped only the "city" text from all the UFO Sightings Reports happening since 1980)
1980-1984 City
```{r}
library(rvest)
library(dplyr)

months <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12")
ufo_1980 <- c()

for (i in 1980:1984){
  for (j in months){
    link <- paste0("https://nuforc.org/webreports/ndxe", i, j, ".html")
    ufo_city_link <- read_html(link)
    ufo_city_link <-  ufo_city_link %>% 
    html_elements("td") %>% 
    html_text()
    ufo_city_1980 <- ufo_city_link[seq(from = 2, to = length(ufo_city_link), by = 9)]
    for (k in ufo_city_1980){
      if ("(" %in% unlist(strsplit(k, ""))){
      next
    }
      ufo_1980 <- c(ufo_1980, k)
    }
  }
}
df_1980 <- data.frame(city=ufo_1980, count=rep(1, length(ufo_1980)))
#df_1980 <- df_1980 %>% 
  #group_by(city) %>% 
  #summarise(count=sum(count))
df_1980$year <- rep("1980", length(df_1980$city))
```

1985-1989 City
```{r}
ufo_1985 <- c()

for (i in 1985:1989){
  for (j in months){
    link <- paste0("https://nuforc.org/webreports/ndxe", i, j, ".html")
    ufo_city_link <- read_html(link)
    ufo_city_link <-  ufo_city_link %>% 
    html_elements("td") %>% 
    html_text()
    ufo_city_1985 <- ufo_city_link[seq(from = 2, to = length(ufo_city_link), by = 9)]
    for (k in ufo_city_1985){
      if ("(" %in% unlist(strsplit(k, ""))){
      next
    }
      ufo_1985 <- c(ufo_1985, k)
    }
  }
}
df_1985 <- data.frame(city=ufo_1985, count=rep(1, length(ufo_1985)))
#df_1985 <- df_1985 %>% 
  #group_by(city) %>% 
  #summarise(count=sum(count))
df_1985$year <- rep("1985", length(df_1985$city))
```

1990-1995 City
```{r}
ufo_1990 <- c()

for (i in 1990:1994){
  for (j in months){
    link <- paste0("https://nuforc.org/webreports/ndxe", i, j, ".html")
    ufo_city_link <- read_html(link)
    ufo_city_link <-  ufo_city_link %>% 
    html_elements("td") %>% 
    html_text()
    ufo_city_1990 <- ufo_city_link[seq(from = 2, to = length(ufo_city_link), by = 9)]
    for (k in ufo_city_1990){
      if ("(" %in% unlist(strsplit(k, ""))){
      next
    }
      ufo_1990 <- c(ufo_1990, k)
    }
  }
}
df_1990 <- data.frame(city=ufo_1990, count=rep(1, length(ufo_1990)))
#df_1990 <- df_1990 %>% 
  #group_by(city) %>% 
  #summarise(count=sum(count))
df_1990$year <- rep("1990", length(df_1990$city))
```

1995-1999 City
```{r}
ufo_1995 <- c()

for (i in 1995:1999){
  for (j in months){
    link <- paste0("https://nuforc.org/webreports/ndxe", i, j, ".html")
    ufo_city_link <- read_html(link)
    ufo_city_link <-  ufo_city_link %>% 
    html_elements("td") %>% 
    html_text()
    ufo_city_1995 <- ufo_city_link[seq(from = 2, to = length(ufo_city_link), by = 9)]
    for (k in ufo_city_1995){
      if ("(" %in% unlist(strsplit(k, ""))){
      next
    }
      ufo_1995 <- c(ufo_1995, k)
    }
  }
}
df_1995 <- data.frame(city=ufo_1995, count=rep(1, length(ufo_1995)))
#df_1995 <- df_1995 %>% 
  #group_by(city) %>% 
  #summarise(count=sum(count))
df_1995$year <- rep("1995", length(df_1995$city))
```

2000-2004 City
```{r}
ufo_2000 <- c()

for (i in 2000:2004){
  for (j in months){
    link <- paste0("https://nuforc.org/webreports/ndxe", i, j, ".html")
    ufo_city_link <- read_html(link)
    ufo_city_link <-  ufo_city_link %>% 
    html_elements("td") %>% 
    html_text()
    ufo_city_2000 <- ufo_city_link[seq(from = 2, to = length(ufo_city_link), by = 9)]
    for (k in ufo_city_2000){
      if ("(" %in% unlist(strsplit(k, ""))){
      next
    }
      ufo_2000 <- c(ufo_2000, k)
    }
  }
}

df_2000 <- data.frame(city=ufo_2000, count=rep(1, length(ufo_2000)))
#df_2000 <- df_2000 %>% 
  #group_by(city) %>% 
  #summarise(count=sum(count))
df_2000$year <- rep("2000", length(df_2000$city))
```

2005-2009 City
```{r}
ufo_2005 <- c()

for (i in 2005:2009){
  for (j in months){
    link <- paste0("https://nuforc.org/webreports/ndxe", i, j, ".html")
    ufo_city_link <- read_html(link)
    ufo_city_link <-  ufo_city_link %>% 
    html_elements("td") %>% 
    html_text()
    ufo_city_2005 <- ufo_city_link[seq(from = 2, to = length(ufo_city_link), by = 9)]
    for (k in ufo_city_2005){
      if ("(" %in% unlist(strsplit(k, ""))){
      next
    }
      ufo_2005 <- c(ufo_2005, k)
    }
  }
}

df_2005 <- data.frame(city=ufo_2005, count=rep(1, length(ufo_2005)))
#df_2005 <- df_2005 %>% 
  #group_by(city) %>% 
  #summarise(count=sum(count))
df_2005$year <- rep("2005", length(df_2005$city))
```

2010-2014 City
```{r}
ufo_2010 <- c()

for (i in 2010:2014){
  for (j in months){
    link <- paste0("https://nuforc.org/webreports/ndxe", i, j, ".html")
    ufo_city_link <- read_html(link)
    ufo_city_link <-  ufo_city_link %>% 
    html_elements("td") %>% 
    html_text()
    ufo_city_2010 <- ufo_city_link[seq(from = 2, to = length(ufo_city_link), by = 9)]
    for (k in ufo_city_2010){
      if ("(" %in% unlist(strsplit(k, ""))){
      next
    }
      ufo_2010 <- c(ufo_2010, k)
    }
  }
}

df_2010 <- data.frame(city=ufo_2010, count=rep(1, length(ufo_2010)))
#df_2010 <- df_2010 %>% 
  #group_by(city) %>% 
  #summarise(count=sum(count))
df_2010$year <- rep("2010", length(df_2010$city))
```

2015-2020 City
```{r}
ufo_2015 <- c()

for (i in 2015:2020){
  for (j in months){
    link <- paste0("https://nuforc.org/webreports/ndxe", i, j, ".html")
    ufo_city_link <- read_html(link)
    ufo_city_link <-  ufo_city_link %>% 
    html_elements("td") %>% 
    html_text()
    ufo_city_2015 <- ufo_city_link[seq(from = 2, to = length(ufo_city_link), by = 9)]
    for (k in ufo_city_2015){
      if ("(" %in% unlist(strsplit(k, ""))){
      next
    }
      ufo_2015 <- c(ufo_2015, k)
    }
  }
}

df_2015 <- data.frame(city=ufo_2015, count=rep(1, length(ufo_2015)))
#df_2015 <- df_2015 %>% 
  #group_by(city) %>% 
  #summarise(count=sum(count))
df_2015$year <- rep("2015", length(df_2015$city))
```


## Combine 1984 - 2022 City data and export to excel
```{r}
df_40 <- data.frame()
df_40 <- rbind(df_40, df_1980)
df_40 <- rbind(df_40, df_1985)
df_40 <- rbind(df_40, df_1990)
df_40 <- rbind(df_40, df_1995)
df_40 <- rbind(df_40, df_2000)
df_40 <- rbind(df_40, df_2005)
df_40 <- rbind(df_40, df_2010)
df_40 <- rbind(df_40, df_2015)

library(openxlsx)
write.xlsx(df_40, "/Users/zhuguanyu/Desktop/df_40.xlsx", rowNames = FALSE)
```



